Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Adding a bit on reference to prior studies.

\subsection{ROUGH: Methodology Motivation} %LL: this text was previously inside related work
{\color{red} Note: this section is a placeholder. Maybe we should put as a subsection inside the methodology section. TODO: reword so that these works seem not like related work, but as motivation for our methodology; i.e. ``here are two methodologies from relevant work swe chose to use for reasons.'' We can also say that we extend their works.}

\subsubsection{Smartphone User Concerns} %LL: this text was previously inside related work
Among such studies, Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

>>>>

\subsection{ROUGH: Methodology Motivation}

\subsubsection{Smartphone User Concerns}
Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
Our methodology follows that study closely, but with a different set of scenarios that are appropriate to wearable devices.
